\section{Background}\label{sec:background}

\subsection{Unmanned Vehicles in Search and Rescue}\label{subsec:unmanned-vehicles-in-search-and-rescue}

Unmanned vehicles have long been used as force multipliers in SAR situations.
\cite{waharte2010supporting} shows that autonomous use of UAVs could significantly enhance terrestrial SAR through structured search strategies, reducing expected detection times compared to random search.
In the maritime domain, recent SAR frameworks (\cite{messmer2024uavassistedmaritimesearchrescue}) for UAV-assisted MSAR have proposed software architectures that combine onboard UAV detection with more advanced ground-station processing.

\cite{7761074} demonstrated a co-operative multi-robot team for surveilling shipwreck survivors at sea, in collaboration with the Portuguese Navy, at an undeclared location.
While the paper offered promising results for the application of UAVs/USVs in Maritime Search and Rescue, many such deployments retain strong human involvement at the control level.
In the case of this paper, a UAV takes off from the USV, ascends to a given height, and then pings a USV with the location of anything it suspects to be a person at sea.
The USV then moves to the target, and takes a picture of it, which is then sent with the target's location to a human operator for verification.

While this system is effective, it relies on a human operator, or a team of operators, to manage the drones in small groups.
This can be due to regulatory constraints, safety concerns, and incomplete foundations for trust in onboard autonomy.

This reliance on manual control helps to explain why many implementations of UAVs in MSAR do not use entirely autonomous solutions.
Factors like safety, certification, and legal accountability inherently favour conservative, operator-centric control approaches.
Consequently, there is little empirical evidence on how far autonomy and human-swarm interfaces can be pushed while maintaining acceptable workload and safety during a Maritime Search and Rescue operation.

\subsection{Swarm Coordination}\label{subsec:swarm-coordination}

Multi-agent swarm coordination is a well-studied topic which aims to achieve a robust method of coordinating multiple agents without single points of failure.
\cite{ENMASCA2025} introduced ``EN-MASCA'' (Enhanced Multi-Agent Swarm Control Algorithm) for drone swarm patrolling in durian orchards.
It employs reinforcement learning approaches to optimise formations and avoid obstacles in terrestrial agricultural settings.

While not related to the maritime domain, EN-MASCA shows that learned coordination can be deployed practically.
However, this comes with the drawback of requiring substantial training data, and computation resources.
Both of these issues can be prohibitive for SAR platforms.

Consensus-based approaches, like the one proposed by~\cite{dev2025swarnraft}, offer a more lightweight alternative to reinforcement learning.
A consensus-based approach tackles robustness to communication issues by allowing multiple drones to converge on a common estimate of the swarm state rather than rely on excessive ground-station communication.

Across these approaches, the most primary motivators appear to be collision avoidance and maximizing search coverage.
Operators over open ocean may not need to worry about terrain, but care must be given to avoid obstacles like ships, waves, and other drones.

BEACON has opted for a geometric, explainable method.
We have chosen to combine a weighted Voronoi Tessellation approach to generate ``cells'' on the map, which are assigned to drones based on their position, and their speed, in such a manner that every drone completes their task at roughly the same time.
Within these cells, drones are given a set of waypoints to follow, which are generated using the ``Boustrophedon`` (Also known as the Lawnmower) path planning algorithm.
While this approach is less adaptable than EN-MASCA-style systems in other scenarios, their behavior is easy for operators to understand and predict, a critical factor in time-critical Maritime Search and Rescue operations.

\subsection{Digital Twins: Definitions, Abstractions, and MSAR}\label{subsec:digital-twins:-definitions-abstractions-and-msar}
Digital Twins are commonly described as digital representations of physical assets or processes that remain synchronized with its real-world counterpart.
These are, notably, different from Digital Models (no data link), Digital Shadows (one-way physical-to-digital data link).

DTs can reduce cognitive workload by abstracting away low-level details, outsourcing tasks like aggregating different sensor streams/assorted metrics, enable predictive analysis, and supporting decision-making tools like path planners and alert systems.
These tools can then act consistently and transparently on behalf of the human supervisor.
In maritime applications, DTs have been used to optimise ship routes, monitor vessel health via operational metrics, with a focus on engineering and maintenance applications~\cite{DT_maritime_applications}.

BEACON adopts the ideas of DT in its layered architecture and decision-support functions, but it does not implement a real-time data link with physical drones, and instead simulates the drone swarm within the application itself.
This decision was made to focus on the design of the interface, and the swarm coordination algorithms, without needing to worry about the technical challenges of real-time data synchronization, which will be implemented in future work.
It's therefore best described as a ``Digital Model/Shadow'' prototype, in that it's a high-fidelity simulation of a physical system with the accompanying User Interface (UI) that is designed to be part of a full Digital Twin system.
Being explicit about this scoping decision is important, to avoid conflating simulation with operational deployment and to focus on human-operator workload mitigation and the design of the human-swarm interface.

\subsection{HCI in Supervisory Control Systems}\label{subsec:supervisory-hci}

HCI research for supervisory control systems focuses on designing interfaces for human operators who oversee and manage autonomous systems.
\cite{AUTOMATIONEFFECTONUAVROUTING} found that excessively automated, simplistic displays can inadvertently increase operator workload by making debugging difficult, reducing situational awareness, and encouraging automation bias.
\cite{CUMMINGS2007339} found that operators supervising multiple UAVs, while experiencing high workload, would adopt load-shedding strategies, where they compartmentalize their attention to a small set of drones.

BEACON's interface combines an emphasis on revealing structure with constraints from research on supervisory control that warn against overly-complex global views of the system.
The mission map and coverage overlays act as configurable displays of our spatial constraints, like the mission boundary, Voronoi cells, and drone paths, while alerts and on-map notifications provide localised information.
The layout's design would be guided by various display design principles, like the Proximity Compatibility Principle.

\subsection{Workload Measurement and NASA-TLX}\label{subsec:workload-measurement-and-nasa-tlx}

NASA-TLX (Task Load Index) is a widely-used subjective workload assessment tool that measures perceived workload across a set of dimensions:

\begin{itemize}
    \item Mental Demand - How mentally demanding was the task?
    \item Physical Demand - How physically demanding was the task?
    \item Temporal Demand - How hurried or rushed was the pace of the task?
    \item Performance - How successful were you in accomplishing what you were asked to do?
    \item Effort - How hard did you have to work to accomplish your level of performance?
    \item Frustration Level - How insecure, discouraged, irritated, stressed, and annoyed were you?
\end{itemize}

Each dimension is rated on a scale from 0 to 100, and then weighted based on pairwise comparisons to determine the relative importance of one dimension over another.

Recent reviews of NASA-TLX, however, have raised concerns about NASA-TLX's conceptual clarity, and its validity in interactive applications.
Systematic analyses of NASA-TLX have found that many studies use it without clearly defining workload, and apply inconsistent weightings, leading to difficulties in reproducing and comparing the results.

BEACON chooses to adopt NASA-TLX despite these caveats due to its widespread use and acceptance in human workload assessment, its clean mapping to MSAR-like supervision, where mental and temporal demand, effort and frustration are particularly important.
It is also practical for repeated use in simulation, and can be easily implemented.
At the same time, TLX scores are interpreted cautiously and are always complemented with objective operational metrics like alert burden, and intervention rate, in line with the recommendations given by~\cite{BABAEI2025103515}.
