\section{introduction}\label{sec:introduction}

\subsection{Motivation}\label{subsec:motivation}

Search and Rescue (SAR) operations are characterized by their inherent urgency and uncertainty.
Empirical analyses of SAR missions indicate that the likelihood of survival declines sharply as search time increases, to the point that missions may eventually become futile if continued indefinitely.
In the context of maritime incidents, survival and resuscitation probabilities are strongly linked to the duration of time spent submerged or exposed.
For example, ~\cite{RN2}, states that the probability of survival/resuscitation decreases significantly after 30 minutes of submersion at >6°C, and after 90 minutes at <6°C\@.

Traditional Maritime Search and Rescue (MSAR) relies on crewed helicopters, vessels, and aircraft.
Keeping these assets at ``full readiness'', which in the context of MSAR means they must be adequately maintained, crewed, fuelled, and immediately deployable, can be difficult if not economically impossible in some regions.
Delays due to limited readiness directly translate into an increase in response time, as time that should be spent on the operation is spent remediating issues at sea, which could lead to a decrease in survival rates.

Research into the Human operators indicates the cognitive and physical demands of MSAR operations can lead to degraded performance.
\cite{riverine_MSAR_stress} directly reports that conditions combining higher physiological stress (like an increased heart rate) and distraction lead to lowered search success.
The paper interprets this as MSAR performance, at least in a riverine context, is significantly impacted by distraction, fatigue, and overwork.
Operators reporting neither stress nor exertion located 78\% of deployed targets, while crew reporting both conditions located only 57\%.
Operators reporting only Exertion located 70\% of targets, while those reporting only Distraction located 57\% of targets.
While the paper stops short of claiming a perfectly isolated causal relationship due to factors like experience, and other pre-SAR factors, it does suggest that the physical and cognitive demands of MSAR are impacted by the conditions of the operators, and that these conditions could be improved leading to better performance from the operators.

~\cite{7761074} shows that Unmanned Aerial Vehicles(UAVs) and Unmanned Surface Vessels(USVs) can be used to augment MSAR operations, by providing rapid aerial and surface coverage.
However, this system remained non-autonomous or semi-autonomous, relying on a team of human operators to control the drones either one-to-one or in small groups.
This would occur due to regulatory constraints, safety concerns, and incomplete trust in onboard autonomy.

As the number of involved drones increases, these control schemes would struggle to scale, facing manpower issues, and cognitive workload from inter-operator coordination.
Digital Twin(DT) frameworks promise to ease these issues by aggregating state information, predicting behavior, and supporting decision-making within a single interactive model.

BEACON aims to explore how DT-inspired architectures and HCI principles can be combined to support a single operator supervising a co-ordinated swarm of autonomous drones, in an MSAR-like scenario.

\subsection{Contributions}\label{subsec:contributions}
This project seeks to contribute the following:

\begin{itemize}
    \item A Digital Twin-inspired Architecture for MSAR drone swarms,
    \item A workload-aware mission-control interface,
    \item An evaluation framework integrated into the application, using subjective tools like NASA-TLX and objective operational metrics,
    \item A study of DT and supervisory-HCI literature in the context of the applications.
\end{itemize}

